\newpage

\section{Obstacle Evasion Course}

The event “Obstacle Evasion Course” extends the track of the Free Drive event
with additional elements which need to be considered during the driving task.
Static and dynamic obstacles are added to the rural road scenario.
\HighlightNew{Additionally, the vehicle has to perform automatic parking
	maneuvers by finding a suitable parking spot inside a parking lot.} The track
does additionally contain at least one suburban section at this point. All
definitions concerning the course of the road maintain validity. There will be
at least 1000 mm track length between obstacles. The additional elements are
spaced at least 1000 mm apart as well and do not overlap. Oncoming traffic is
not to be expected, except when passing barred areas inside the suburban
scenario.

\subsubsection{Suburban Scenario}
\label{suburban_area}

The suburban area is a special section of the track, containing additional
elements compared to the track design of the rural road scenario. Beginning and
end of suburban areas are defined by markings on the road surface (cf. Section
\ref{fig_road_markings}) and according traffic signs (cf. Section
\ref{traffic_signs}). \HighlightNew{The suburban area containins a parking lot
	which is indicated by the parking traffic sign.} (cf. Section
\ref{fig_parking_lot})

The speed limit within the suburban section, as indicated by the traffic signs
has to be scaled by 1:10 (i.e. a speed limit of 30 km/h corresponds to 0.83
m/s). In addition to the speed limits depicted in the signs marking the
suburban scenario, other numeric signs in steps of 10 km/h might appear (e.g. a
speed limit of 20 km/h). Speed limit zones begin and end at the road markings,
as depicted in Section \ref{fig_speed_limit_zone}. The according traffic signs
will be placed at those positions. Elements of the suburban scenario will not
be located on uphill and downhill grades.

\subsection{Elements of the Obstacle Evasion Course}
\label{elements_obstacle_evasion}
\subsubsection{Static Obstacles}

During this event, a number of static obstacles will be placed in the right
lane, in the left lane and outside of the track. The body of each obstacle
consists of white cardboard with dimensions as specified in the appendix
(Section \ref{fig_obstacle_dimensions}). Obstacles can be fixed on the ground.
The obstacles are not always placed exactly in a specific lane, however under
no circumstance can both lanes be blocked. In this sense, static obstacles
outside the track are no artifacts in the sense of Section \ref{artifacts}.
Thus, the described minimum distance to lane markings for artifacts does not
apply.

Obstacles may force the vehicle to change lanes. Lane changes must be indicated
using the turn indicators. Passing maneuvers must be executed without touching
an obstacle. They must be completed after a maximum distance of 2 m after
having passed the obstacle.

\subsubsection{Dynamic Obstacles}

Apart from static obstacles, at least one dynamic obstacle is present on the
track. Its shape resembles the static obstacles (“driving white cardboard box”)
and it can be encountered in both lanes and in combination with other track
elements, as long as this is not explicitly excluded. It moves at a speed of
0.6 m/s. Dynamic obstacles do not execute lane changes and do not perform any
passing maneuver. Dynamic obstacles can stop temporarily and potentially block
the right lane. It may be passed, but not in intersections. Passing maneuvers
in intersections are penalized. A dynamic obstacle will not block both lanes in
combination with a static obstacle, unless passing is prohibited in the area
(cf. Section \ref{no_passing_zones}). Thus, allowed passing maneuvers can
always be executed without encountering an obstacle on the left lane. The
passing maneuver is subject to the same regulations as when passing a static
obstacle.

\subsubsection{Intersections of the Rural Road Scenario}
\label{intersection_rural}

Sections of the track can be part of intersections with other parts of the
track. The respective lanes meet at angles between 70° and 90°.

An intersection possesses three to four entries or exits respectively. Design
and layout of the intersections of the rural road scenario are shown in the
appendix (Section \ref{intersection_rural}). Left and right lane boundaries of
intersecting lanes can be connected through a rounded transition with a radius
of about 100 mm. Intersections of the rural road scenario must be crossed
driving straight. Entries to intersections can display stop lines. These lines
are 36 mm to 40 mm wide and cross one lane completely.

Additionally, a stop line is complemented by a traffic sign (stop sign, cf.
Section \ref{fig_traffic_signs}). Entries without a stop line are not marked
separately. The right of way is only announced by the respective traffic sign.
If a stop line is located in the own lane, the vehicle must stop for at least 3
s. The front of the vehicle must be located in front of the stop line, however
the distance must not be greater than 150 mm.

The right of way of a dynamic obstacle must be respected at an intersection, if
the dynamic obstacle is located within the defined area (cf. Section
\ref{fig_intersection_give_way}). If the vehicle does not possess the right of
way, it must wait until the dynamic obstacle has completely crossed the
intersection. Only one dynamic obstacle at a time can be present at an
intersection.

\subsubsection{No-Passing Zones}
\label{no_passing_zones}

Sections of the track, not only in the suburban area, can be defined as
no-passing zones. Corresponding traffic signs and lane markings will indicate
such sections (cf. Section \ref{lane_markings}). In sections with a solid
center line (a solid line within a double center line facing the ego lane)
obstacles must not be passed. However, if a passing maneuver has been started
before a no-passing zone, the vehicle is allowed to return to the right lane in
any case.

In a no-passing zone, the dynamic obstacle must be followed at a distance of at
least 300 mm until the end of the zone. Static obstacles will not block the
right lane in no-passing zones. Since passing is prohibited, a combination of a
dynamic obstacle in the right lane and a static object in the left lane can
occur, temporarily blocking the whole track.

\subsubsection{Two-lane Expressway}

Sections of the rural scenario, can be defined as an expressway. The beginning
and end of such sections will be indicated by traffic signs (cf. Section
\ref{fig_traffic_signs}). Expressways are a planar and mostly straight section
of at least 10 m length, without any sharp turns. Any distinctive curve will be
supported with traffic signs, as described in Section \ref{traffic_signs}.
Vehicles on the expressway have right of way, no stop lines will be
encountered. No obstacles will be present in the right lane of this section.
Since the track is assumed to be a two-lane expressway, the vehicles must stay
in the right lane all the time.

\subsection{Additional Elements of the Suburban Scenario}
\label{elements_suburban_scenario}
\subsubsection{Traffic Signs}

In addition to the traffic signs defined in Section \ref{traffic_signs} and
\ref{intersection_rural}, the suburban scenario contains several other traffic
signs which must be respected. Each traffic sign defines the beginning of the
connected elements as defined in the following sections. Traffic signs can only
occur in combination with their connected element. The exact dimensions and
positioning are defined in the appendix of this document (cf. Section
\ref{fig_traffic_signs}). Distances for longitudinal distances are measured on
the right hand lane marking. Each traffic sign of the suburban scenario is
complemented with specific markings on the road surface. Those markings must
not have the same distance to the corresponding element as the traffic sign
(cf. Section \ref{turning}). See the following sections for the according
specifications.

\begin{highlight}
	\subsubsection{Parking Lot}

	Located on the track are parking areas with multiple spots for parallel and
	perpendicular parking. \HighlightNew{Parking areas are announced by the
		corresponding traffic sign.} (cf. Section \ref{fig_parking_lot}) The parking
	area is a planar and straight part of the track with a dashed center line
	without missing lane markings. Additional elements (intersections, missing lane
	markings, traffic signs, etc.) are not present. All areas for parking are
	located in this zone.

	\subsubsection{Parallel Parking}

	Within the parking zone there is at least one parallel parking area next to the
	right lane. White cardboard boxes represent other vehicles. The boxes can be
	fixed to the ground. There is a space of 20 mm to 200 mm between the right lane
	marking and the side of the obstacle which faces the track. The obstacles
	measure at least 100 mm in height and length. The parking area and the track
	are located in the same ground plane. Individual parking spots of the parking
	area can be marked as no parking zones. These areas may not be used for
	parking, but may be used for maneuvering.

	There will be multiple parking spots of different size in the parallel parking
	area(s) next to the track. The left- and right-hand limits of the parking spots
	are defined by the right lane marking and an additional solid white line (also
	18 mm to 20 mm wide). Front and rear limits are defined either by white
	cardboard boxes or by a no parking zone (cf. Section
	\ref{fig_parallel_parking}). \HighlightNew{Approaching from the parking sign,
		the parking spots will be growing in length.} The final and largest spot will
	beat least 700 mm in length. Nevertheless, small distances of under 400 mm
	might be present between obstacles anywhere inside the parallel parking
	area(s).

	\subsubsection{Perpendicular Parking}

	An additional type of parking area within the parking zone consists of several
	parking spots with a perpendicular orientation to the track. Such area is
	located at least once on the left-hand side of the track and may also be used
	for parking.

	All spots have the same size, as shown in Section
	\ref{fig_perpendicular_parking}. The parking spots are separated and limited to
	the front as well as to the rear by 18 mm to 20 mm wide white markings. Parking
	spots can be blocked by obstacles or no parking zones. A parking spot is
	considered to be blocked, if the vehicle cannot be placed completely inside the
	spot. Obstacles possess the same dimensions as in the parallel parking area and
	can be placed at a distance of 20 mm to 100 mm from the solid left lane
	marking.

	For parking, the vehicle must be positioned inside one marked spot that is not
	blocked. Vehicles may move forward or backward into the parking space. The left
	lane of the track may only be crossed during the actual parking maneuver. When
	searching for a parking spot, the vehicle must continue to use the right lane.
\end{highlight}

\subsubsection{Barred Area}

In addition to obstacles, the suburban scenario can contain barred areas on
straight sections of the track. These areas block one lane for a length of max.
2000 mm, measured along the outer lane marking. The areas must be passed just
as a regular obstacle. Barred areas are marked with a 18 mm to 20 mm wide
trapezoidal outline, filled with 36 mm to 40 mm wide white markings with black
spacing. For shape and dimensions see Section \ref{fig_barred_area}. The areas
are at least 150 mm wide and are always connected with the left or right lane
boundaries. Oncoming traffic has the right of way at barred areas, indicated by
a corresponding traffic sign (cf. Section \ref{fig_traffic_signs}).

If a dynamic obstacle is located within 1000 mm of the beginning of the barred
area, the vehicle has to wait. Switching lanes is only allowed with an empty
left lane, oncoming traffic must have completely passed. The desired passing
maneuver has to be indicated while waiting by flashing the left turn
indicators. Only one dynamic obstacle at a time can occur at a barred area. If
the vehicle is able to pass a barred area without leaving the own lane or
driving over the markings, the vehicle may continue along the barred area even
in case of oncoming traffic.

\subsubsection{Crosswalk}

In a suburban area, one or more crosswalks may be present. These are marked
with several 36 mm to 40 mm wide and 400 mm long white markings parallel to the
direction of travel which are spaced 40 mm apart (cf. Section
\ref{fig_crosswalk}). A crosswalk is indicated by a corresponding traffic sign
(cf. Section \ref{fig_traffic_signs}). On the roadside at each crosswalk
“pedestrians” may wait to cross the road. For this purpose two areas are
defined which may contain relevant pedestrians.

A “pedestrian” is depicted by a small white cardboard box in analogy to the
static obstacles. In addition, each pedestrian is marked with a pictograph, in
order to facilitate its detection (cf. Section \ref{fig_pedestrians}). Multiple
pedestrians can be located on the right- as well as on the left-hand side of
the crosswalk. Pedestrians will always be clearly distinguishable from the view
of the approaching vehicle. Only if at least one pedestrian is present in the
defined zones, the vehicle must stop in front of the crosswalk. Stopping must
be performed with the same regulations as at intersections. Pedestrians start
crossing only after the vehicle has stopped. If all relevant pedestrians have
crossed in front of the vehicle, the vehicle may continue. Driving on before
all pedestrians start to cross and have cleared the crosswalk will be
penalized. If no pedestrian is present, the vehicle may slow down, but is not
allowed to come to a complete stop. No points will be given in this case.

\subsubsection{Extended Regulations at Intersections}

In addition to the requirements arising from stop lines, there can be different
regulations for the right of way at intersections in the suburban scenario.
Three types of intersections have to be considered:

\begin{itemize}
	\item Intersections with stop lines (cf. Section \ref{intersection_rural})
	\item Intersections with priority road and give-way lines
	\item Intersections without regulations by road markings or signs (priority to the
	      right)
\end{itemize}

Dimensions and layout of the additional intersections are displayed in the
appendix (cf. Section \ref{additional_intersections}). Stop lines and give-way
lines at priority roads are also announced by traffic signs (cf. Sections
\ref{fig_traffic_signs}). A give-way line is 36 mm to 40 mm wide and consists
of 80 mm long dashes, interrupted by 60 mm long gaps. Stop and give-way lines
occur in pairs at opposing intersection entries, unless the priority road
displays a mandatory direction and requires turning (cf. next Section). At a
give-way line, the vehicle must stop for at least 1 s.

Dynamic obstacles must be considered in any type of intersection. If an
intersection does not contain any indication of priority by road markings or
signs, priority to the right is to be applied. There will be no traffic signs
to announce such intersections, while all four arms of the intersection will
display a give-way line. The requirement to stop and potentially give the right
of way to dynamic obstacles must still be respected. Scenarios which yield
ambiguous regulations of the right of way will not be encountered.

\subsubsection{Turning}
\label{turning}

In addition to the intersections described above, intersections in the suburban
scenario can have a mandatory direction to cross the intersection. Different
scenarios are shown in Section \ref{fig_intersection_mandatory}. This will be
announced by a corresponding traffic sign and a marking on the road surface
(cf. Sections \ref{traffic_signs} and \ref{fig_road_markings}). Vehicles will
have to turn left or right according to these regulations \HighlightNew{and
	signal this accordingly with their turn indicators}. In the intersection, the
mandatory direction will additionally be indicated by dashed turn lines that
continue the center line and the right lane boundary. Turn lines cannot be
missing.

\subsubsection{Speed Limits}

Within a suburban area, the vehicle has to adhere to the given speed limit.
Devices for measuring the speed of the vehicle might be present.

\subsection{Execution of the Event}

\subsubsection{Start}

The starting order of the teams will be announced by the commission, visualized
using the start scheduling system (cf. Section \ref{start_scheduling}) during
the competition. The vehicle must be placed in the start box, located next to
the track (cf. Section \ref{start_box}). The attempt is started by a judge or a
referee, signaled by the opening of the start box gate.\\ It is not strictly
necessary to detect the presence of the markings on the gate, the vehicle only
has to detect when the gate is opened.(cf. Section
\ref{fig_start_box_markings})

\subsubsection{Attempts}

The attempt may be canceled while the gate of the start box is open. The team
is then allowed a second attempt, after all other teams have completed their
first attempt.\\ The commission may arbitrarily choose the time of the second
attempt if this is required to comply with the schedule. The affected team will
be given at least 10 minutes to prepare for the second attempt after being
informed by the commission. The vehicle does not have to be placed back at the
"parc fermé" and may be modified by the team while preparing for the second
attempt. Cancelling an attempt is penalized (cf. Section
\ref{obstacle_scoring}). A missed start results in a second attempt
automatically.

\subsection{RC-Mode}

In case the vehicle is not able to continue following the track on its own, the
team may activate RC-mode in order to get the vehicle back into normal
behavior. If the vehicle does not return into the right driving lane on its
own, RC-mode must be activated immediately. Distances travelled outside of the
driving lane will otherwise be subtracted from the total distance covered.
Bonuses cannot be earned by vehicle behavior shown in RC-mode. Additionally,
skipping challenges of the obstacle course (by not driving in the right lane)
will be punished with the penalty designated for the respective element. Each
activation of RC-mode is penalized. RC-mode is subject to the regulations in
Section \ref{rc_mode}.

\subsection{Parking}
\begin{highlight}
	Parking can be performed once per lap during the Obstacle Evasion Course.

	The vehicle can perform a parking attempt by finding a parking spot within the
	parking areas and maneuvering into it, without touching surrounding obstacles.
	Attempting more than one parking attempt per lap will be penalized. Parking
	spots are indicated by the corresponding traffic sign.\footnote{\HighlightNew{
		Unlike in previous events, the parking area is not guaranteed to be located
		immediately at the beginning of the track. As a result, the starting line can
		not be used as an indicator for the parking area.}}

	The start of a parking maneuver must be signaled using the turn indicators. The
	turn indicators must point in the direction of the parking spot (i.e. blink
	left if the parking spot is to the left of the vehicle).

	A complete parking maneuver requires the vehicle to come to a full stop being
	located in a valid spot \HighlightNew{with all of its wheels} and flash all
	turn indicators at least one time. While maneuvering out of the parking spot,
	the vehicle may cross the left lane, but has to continue driving in the right
	lane after the parking maneuver.

	The correct position of the vehicle will be checked from both sides of the
	track with the first flashing of the indicators. Penalties may apply until the
	vehicle is driving with a positive speed along the route while touching the
	right lane with at least 3 wheels.

	Leaving the outer boundaries of the parking area is penalized the same as
	leaving the right lane while driving. \HighlightNew{The speed in the parking
		lot is limited to the speed on the adjacent road.} Collisions with obstacles
	during the parking maneuver will be penalized.
\end{highlight}

\subsection{Scoring}{
	\label{obstacle_scoring}

	\renewcommand*\footnoterule{} % No line above footnotes
	\newcommand{\topstrut}{\rule{0pt}{3.5ex}}
	\rowcolors{0}{white}{lightgray!40} % Alternate row colors

	Each team will start the event with a fixed number of base points. The base
	points are predetermined by the commission and will depend on the length of the
	track and the number of occuring elements. The total distance covered by the
	vehicle will have no influence on the scoring.

	\subsubsection{Timing}
	Each team will be given a \textbf{5-minute time limit} to complete
	\textbf{three laps} around the track. After the vehicle has completed all three
	laps, the attempt is over and no further points will be awarded. Timing of the
	event starts with the opening of the start box gate, described in section
	\ref{start_box}.

	\subsubsection{Evaluation}
	When the vehicle passes one of the elements described in section
	\ref{elements_obstacle_evasion} and \ref{elements_suburban_scenario}, it will
	receive either a positive, neutral or negative evaluation.

	Any time the vehicle complies with all the requirements of a certain element,
	it will receive a positive evaluation and gain points.\\ If the vehicle fails
	to comply with any of the requirements, it will generally receive a neutral
	evaluation and no points will be awarded.\\ In some cases, the vehicle may
	receive a negative evaluation and points will be deducted.

	The following section \ref{obstacle_scoring_guidelines} provides an overview of
	the scoring guidelines for each element. The bottom row of each table shows the
	amount of points that will be awarded or deducted for each evaluation.

	The final score of each team will be the sum of the base points and the points
	gained or lost during the event. Only after a vehicle has completed at least
	one full lap will the attempt be valid and any points awarded. In case the
	vehicle has left the track or skipped certain parts of it, the commission will
	decide whether the attempt was valid.

	\newpage

	\subsection{Scoring Guidelines}
	\label{obstacle_scoring_guidelines}

	\subsubsection*{Static Obstacles}
	\begin{table}[H]
		\begin{tabularx}{\textwidth}{XXX}
			\toprule
			\textbf{Positive}                & \textbf{Neutral}             & \textbf{Negative}          \\
			\midrule
			Successfully passed the obstacle & Merging distance > 2m        & Collision with an obstacle \\
			\topstrut
			\textbf{+10}                     & \textbf{0}                   & \textbf{-10}               \\
			\bottomrule
		\end{tabularx}
	\end{table}

	\subsubsection*{Dynamic Obstacles}
	\begin{table}[H]
		\begin{tabularx}{\textwidth}{XXX}
			\toprule
			\textbf{Positive}                & \textbf{Neutral}                        & \textbf{Negative}          \\
			\midrule
			Successfully passed the obstacle & Merging distance > 2m                   & Collision with an obstacle \\
			                                 & Passed the obstacle in an intersection  &                            \\
			\topstrut
			\textbf{+15}                     & \textbf{0}                              & \textbf{-10}               \\
			\bottomrule
		\end{tabularx}
	\end{table}

	\begin{highlight}
		\subsubsection*{Obstacles at Intersections}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}          & \textbf{Neutral}                                & \textbf{Negative}          \\
				\midrule
				Respected the right-of-way \footnotemark[2] & Did not respect right-of-way \footnotemark[2]                    & Collision with an obstacle \\
				                           & Obstacle has not fully cleared the intersection &                            \\
				\topstrut
				\textbf{+10}               & \textbf{0}                                      & \textbf{-10}               \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{Oncoming Obstacles}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                           & \textbf{Neutral}             & \textbf{Negative}          \\
				\midrule
				Respected the right-of-way \footnotemark[2] & Did not respect right-of-way \footnotemark[2] & Collision with an obstacle \\
				\topstrut
				\textbf{+5}                                 & \textbf{0}                   & \textbf{-10}               \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\footnotetext[2]{If the obstacle has the right-of-way, e.g. at a barred area, priority-to-right, ...}
		\newpage

		\subsubsection*{Drive Straight Stop/Give-Way Intersection}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                      & \textbf{Neutral}                           & \textbf{Negative}                              \\
				\midrule
				Stopped at the stop or give-way line   & Distance from stop or give-way line > 15cm & Did not stop at the stop line \footnotemark[3] \\
				Went straight through the intersection & Turned at the intersection                 &                                                \\
				                                       & Stopped for < 3s at stop line              &                                                \\
				                                       & Stopped for < 1s at give-way line          &                                                \\
				\topstrut
				\textbf{+5}                            & \textbf{0}                                 & \textbf{-5}                                    \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{Drive Straight Priority-to-Right Intersection}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                      & \textbf{Neutral}                   & \textbf{Negative}                    \\
				\midrule
				Stopped at the give-way line           & Distance from give-way line > 15cm &                                      \\
				Went straight through the intersection & Turned at the intersection         &                                      \\
				                                       & Stopped for < 1s at give-way line  &                                      \\

				\topstrut
				\textbf{+10}                           & \textbf{0}                         & \textit{No negative points possible} \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{\HighlightChange{Mandatory Turn Stop/Give-Way Intersection}}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                    & \textbf{Neutral}                           & \textbf{Negative}                              \\
				\midrule
				Stopped at the stop or give-way line & Distance from stop or give-way line > 15cm & Did not stop at the stop line \footnotemark[3] \\
				Took the correct turn                & Made a wrong turn \footnotemark[4]         &                                                \\
				                                     & Stopped for < 3s at stop line              &                                                \\
				                                     & Stopped for < 1s at give-way line          &                                                \\
				\topstrut
				\textbf{+15}                         & \textbf{0}                                 & \textbf{-5}                                    \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{\HighlightChange{Mandatory Turn Priority-to-Right Intersection}}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}        & \textbf{Neutral}                   & \textbf{Negative}                    \\
				\midrule
				Stopped at give-way line & Distance from give-way line > 15cm &                                      \\
				Took the correct turn    & Made a wrong turn \footnotemark[4] &                                      \\
				                         & Stopped for < 1s at give-way line  &                                      \\
				\topstrut
				\textbf{+15}             & \textbf{0}                         & \textit{No negative points possible} \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\footnotetext[3]{Only applies for stop and not for give-way line}
		\footnotetext[4]{Includes driving straight incorrectly}
		\newpage

		\subsubsection*{Parking}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                                        & \textbf{Neutral}                               & \textbf{Negative}          \\
				\midrule
				Parked correctly in the parking lot                      & Not parked correctly                           & Collision with an obstacle \\
				All wheels are within the boundaries of the parking spot & No or more than one parking maneuver performed &                            \\
				\topstrut
				\textbf{+20}                                             & \textbf{0}                                     & \textbf{-10}               \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{No-Passing Zones}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}                   & \textbf{Neutral}            & \textbf{Negative}                                    \\
				\midrule
				Did not cross the solid center line & Distance to obstacle < 30cm & Crossed the solid center line with more than 1 wheel \\
				Distance to obstacle > 30cm         &                             &                                                      \\
				\topstrut
				\textbf{+5}                         & \textbf{0}                  & \textbf{-10}                                         \\
				\bottomrule
			\end{tabularx}
		\end{table}

		\subsubsection*{Barred Area}
		\begin{table}[H]
			\begin{tabularx}{\textwidth}{XXX}
				\toprule
				\textbf{Positive}              & \textbf{Neutral}             & \textbf{Negative}                    \\
				\midrule
				Did not enter the barred area  & Entered the barred area      &                                      \\
				\topstrut
				\textbf{+10}                   & \textbf{0}                   & \textit{No negative points possible} \\
				\bottomrule
			\end{tabularx}
		\end{table}
	\end{highlight}

	\subsubsection*{Crosswalk with Pedestrian(s)}
	\begin{table}[H]
		\begin{tabularx}{\textwidth}{XXX}
			\toprule
			\textbf{Positive}                         & \textbf{Neutral}                                    & \textbf{Negative}           \\
			\midrule
			Stopped at the crosswalk                  & Stopped for < 3s at the crosswalk                   & Collision with a pedestrian \\
			Pedestrians have cleared the crosswalk    & Distance from the crosswalk > 15cm                  &                             \\
			                                          & Pedestrians have not fully cleared the crosswalk    &                             \\
			\topstrut
			\textbf{+15}                              & \textbf{0}                                          & \textbf{-10}                \\
			\bottomrule
		\end{tabularx}
	\end{table}

	\subsubsection*{\HighlightChange{Crosswalk without Pedestrians}}
	\begin{table}[H]
		\begin{tabularx}{\textwidth}{XXX}
			\toprule
			\textbf{Positive}             & \textbf{Neutral}         & \textbf{Negative}                     \\
			\midrule
			Did not stop at the crosswalk & Stopped at the crosswalk &                                       \\
			\topstrut
			\textbf{+10}                  & \textbf{0}               &  \textit{No negative points possible} \\
			\bottomrule
		\end{tabularx}
	\end{table}

	\newpage

	\subsection*{Additional Penalties}
	\begin{table}[H]
		\begin{tabular}{@{}lccc@{}}
			\toprule
			\textbf{Violation}            & \textbf{Maximum Count} &  & \textbf{Penalty}   \\
			\midrule
			Second Attempt                & 1                      &  & -0.5 x base points \\
			Active WiFi Connection        & 1                      &  & -0.5 x base points \\
			Exceeding Speed-Limit         & $\infty$               &  & \HighlightNew{-5}  \\
			Activation of RC-Mode         & $\infty$               &  & -5                 \\
			Leaving the right lane        & 10                     &  & \HighlightNew{-2}  \\
			Collision with road sign      & $\infty$               &  & -5                 \\
			Falsely using turn indicators & 10                     &  & \HighlightNew{-2}  \\
			\bottomrule
		\end{tabular}
	\end{table}
	\clearpage
}