\chapter{Prerequisites for Attending}

Only students fulfilling the following conditions are allowed to participate in
the CAuDri-Challenge.

\section{Status of Enrollment}

Every participant must either be currently enrolled in a Bachelor’s, Master’s
or a comparable degree program or the respective degree must not have been
obtained more than six months before the competition. There is no restriction
concerning the subject of study. Research staff and PhD students may not
participate actively in conceptualization or development of the vehicle. They
may not participate actively in the competition (cf. Section
\ref{dev_know_how}).\\
\colorbox{yellow}{\parbox{\colorboxwidth}{No proof of enrollment is required
for registration, but teams must provide it if requested by the regulations
commission.}}

\section{Minimum Age}

There is no minimum age for participation. Underage participants must submit a non formal written declaration of consent signed by their legal guardian.

\section{Number of Teams per Institution}

The number of teams per institution is not limited. However, the development of
the vehicles must be strictly separated. Software and hardware architectures of
the respective teams must differ significantly.

\section{Publication Rights}

By registering, every team and every participant declares their agreement with
the publication of image, video and audio recordings. This also includes the
recording of team presentations. This agreement might be revoked until the day
of the competition.