\chapter{Regulations}

\section{Commission}

Rules and obligations of the CAuDri-Challenge can only be modified by the
CAuDri-Challenge Regulations Commission. \colorbox{yellow}{The commission is elected by the 
CAuDri e.v. and published in advance of the competition.} In cases of uncertainty or discrepancy 
the commission is responsible for official statements.

\section{Validity of Regulations}

Only the regulations which have been published on the official website are
valid for the competition. Old Regulations are invalidated, as soon as a new
version of the regulations is published. Updates of the regulations will
additionally be announced to registered teams.

\section{Questions}

Every participant is obliged to thoroughly read, understand, and accept the
regulations. In case of questions, the commission is to be consulted. Questions
can either be directly posed to the commission or be published in the official
CAuDri-Challenge Discord server regulations channel.

Studying the regulations channel is recommended, as questions are being
publicly discussed there on a regular basis.

\section{Authority}

The commission can change the schedule or the regulations of the event at any
time. All participants are obliged to cooperate with the commission and follow
their instructions.

\section{Limit of participating teams}

The commission reserves the right to limit the number of participating teams if
this becomes necessary due to organizational reasons. In case of such a limit
additional qualifying tasks may be requested from the teams.